In-silico molecular enrichment and clearance of the human intracranial space

### 2024-12-07 paper/supplementary_main.tex

%% Both $\Omega$ and $\Lambda$ are fixed in time and we assume
%% constant-in- time radii (despite varying radii to drive peristaltic
%% flow, see \cref{sec:sup:peristalsis}).

@@

To model steady flow induced by pressure differences between end nodes
in a perivascular network $\Lambda$, with edges $\{\Lambda^i\}_i$,
internal nodes $\mathcal{B}$ and end nodes $\mathcal{N}$, we consider
the following system of hydraulic network
equations~\cite{tithof2022network, daversin2022geometrically,
  gjerde2024directional}. The unknowns are the PVS flux $\hat{q} :
\Lambda \rightarrow \R$ and pressure $\hat{p} : \Lambda
\rightarrow \R$, which represent the fluid flux and the average
pressure across cross-sections of the PVSs, respectively. These are
defined for each $\Lambda^i$ by solving:
\begin{subequations}
\begin{alignat}{2}
  \hat{q} + \frac{A \kappa}{\mu} \partial_{s} \hat{p} & = 0 &&
  \quad \text{ in } \Lambda^i , \\ 
  - \partial_s \hat{q} & = 0 &&
  \quad \text{ in } \Lambda^i ,  
\end{alignat} 
\label{eq:1d_flow}%
\end{subequations}%
where $A$ is the area of the PVS cross-sections, $\mu$ is the CSF viscosity as before, and $\kappa$ is derived from an assumption of Poiseuille flow in the annular cross-section of the PVS as~\cite{tithof2022network}: 
\begin{equation}
\kappa = \frac18 \left( R_2^2 + R_1^2 - \frac{1}{\ln(R_2/R_1)} (R_2^2- R_1^2) \right). 
\end{equation}
The PVS flux $\hat{q}$ and the associated average PVS velocity in the
axial direction $\hat{u}$ are directly related by the cross-sectional area
\begin{equation}
  \hat{q}^i = A^i \hat{u}^i \qquad \foralls \Lambda^i.
\end{equation}

>>>>

\mk{What is justification of \eqref{eq:1d_bcs}?}
%% Both $\Omega$ and $\Lambda$ are fixed in time and we assume
%% constant-in- time radii (despite varying radii to drive peristaltic
%% flow, see \cref{sec:sup:peristalsis}).

@@

To model steady flow induced by pressure differences between end nodes
in a perivascular network $\Lambda$, with edges $\{\Lambda^i\}_i$,
internal nodes $\mathcal{B}$ and end nodes $\mathcal{N}$, we consider
the following system of hydraulic network
equations~\cite{tithof2022network, daversin2022geometrically,
  gjerde2024directional}. The unknowns are the PVS flux $\hat{q} :
\Lambda \rightarrow \R$ and pressure $\hat{p} : \Lambda
\rightarrow \R$, which represent the fluid flux and the average
pressure across cross-sections of the PVSs, respectively. These are
defined for each $\Lambda^i$ by solving:
\begin{subequations}
\begin{alignat}{2}
  \hat{q} + \frac{A \kappa}{\mu} \partial_{s} \hat{p} & = 0 &&
  \quad \text{ in } \Lambda^i , \\ 
  - \partial_s \hat{q} & = 0 &&
  \quad \text{ in } \Lambda^i ,  
\end{alignat} 
\label{eq:1d_flow}%
\end{subequations}%
where $A$ is the area of the PVS cross-sections, $\mu$ is the CSF viscosity as before, and $\kappa$ is derived from an assumption of Poiseuille flow in the annular cross-section of the PVS as~\cite{tithof2022network}:  \rami{Here,  we consider the steady state  case and we assume that the PVS domain is fixed and not pulsating  }
\begin{equation}
\kappa = \frac18 \left( R_2^2 + R_1^2 - \frac{1}{\ln(R_2/R_1)} (R_2^2- R_1^2) \right). 
\end{equation}
The PVS flux $\hat{q}$ and the associated average PVS velocity in the
axial direction $\hat{u}$ are directly related by the cross-sectional area
\begin{equation}
  \hat{q}^i = A^i \hat{u}^i \qquad \foralls \Lambda^i.
\end{equation}
